---
title: "Assignment 3 - Part 2 - Diagnosing Schizophrenia from Voice"
author: "Asger, Rebecca, Dora, Jana, Sophia"
date: "October 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 3 - Part 2 - Diagnosing schizophrenia from voice

In the previous part of the assignment you generated a bunch of "features", that is, of quantitative descriptors of voice in schizophrenia. We then looked at whether we could replicate results from the previous literature.
We now want to know whether we can automatically diagnose schizophrenia from voice only, that is, relying on the set of features you produced last time, we will try to produce an automated classifier.
Again, remember that the dataset containst 7 studies and 3 languages. Feel free to only include Danish (Study 1-4) if you feel that adds too much complexity.

Issues to be discussed your report:
- Should you run the analysis on all languages/studies at the same time? 
- Choose your best acoustic feature from part 1. How well can you diagnose schizophrenia just using it?
- Identify the best combination of acoustic features to diagnose schizophrenia using logistic regression.
- Discuss the "classification" process: which methods are you using? Which confounds should you be aware of? What are the strength and limitation of the analysis?
- Bonus question: Logistic regression is only one of many classification algorithms. Try using others and compare performance. Some examples: Discriminant Function, Random Forest, Support Vector Machine, etc. The package caret provides them. 
- Bonus Bonus question: It is possible combine the output of multiple  classification models to improve classification accuracy. For inspiration see,
https://machinelearningmastery.com/machine-learning-ensembles-with-r/
 The interested reader might also want to look up 'The BigChaos Solution to the Netflix Grand Prize'

## Learning objectives
- Learn the basics of classification in a machine learning framework
- Design, fit and report logistic regressions
- Apply feature selection techniques

### Let's start

We first want to build a logistic regression to see whether you can diagnose schizophrenia from your best acoustic feature. Let's use the full dataset and calculate the different performance measures (accuracy, sensitivity, specificity, PPV, NPV, ROC curve). You need to think carefully as to how we should (or not) use study and subject ID.

Then cross-validate the logistic regression and re-calculate performance on the testing folds. N.B. The cross-validation functions you already have should be tweaked: you need to calculate these new performance measures. Alternatively, the groupdata2 and cvms package created by Ludvig are an easy solution. 

N.B. the predict() function generates log odds (the full scale between minus and plus infinity). Log odds > 0 indicates a choice of 1, below a choice of 0.
N.N.B. you need to decide whether calculate performance on each single test fold or save all the prediction for test folds in one datase, so to calculate overall performance.
N.N.N.B. Now you have two levels of structure: subject and study. Should this impact your cross-validation?
N.N.N.N.B. A more advanced solution could rely on the tidymodels set of packages (warning: Time-consuming to learn as the documentation is sparse, but totally worth it)



```{r}
# Let's load the data and packages:
pacman::p_load(pacman, backports,tidyverse, stringi, stringr, purrr, lme4, janitor, plyr, caret, e1071, yardstick, boot, cvms, groupdata2, pROC, knitr)


scaled_data <- read.csv("Scaled Data.csv"); scaled_data[,1] <- NULL ; scaled_data$soundname <- NULL ; scaled_data$Study <- scaled_data$Study %>% as.factor()


# Making a model with speechrate as a predictor of diagnosis, descriminating for each study.
sr_pred <- glm(Diagnosis ~ 0 + Study + Study:Speechrate, family = "binomial", data = scaled_data)
summary(sr_pred) # Most of the studies have a negative slope (and study 6 has a very small positive one). Of the 7 studies, studies 2,3,4 and 7 show significant relations between speechrate and logOdds of being schizophrenic. SPecifically, as speechrate increases, participants are *slightly* less likely to be schizophrenic.


# We have decided to exclude studies that are not in Danish, as by doing so we can decide not to discriminate by study, as the heterogeneity due to different speechrates etc. of different languages is not present. By adding all the danish studies together, we also achieve a larger dataset. We assume that the methodologies (data collection procedures, etc.) of the Danish studies are essentially comparable.

# Filtering study 5, 6 and 7 away.
danish_data <- scaled_data %>% filter(Study != 5) %>% filter(Study != 6) %>% filter(Study != 7)

# Now we try to make a model of diagnosis and speechrate using only the danish data.
sr_pred <- glm(Diagnosis ~ Speechrate, family = "binomial", data = danish_data)
summary(sr_pred)
# Significant results; as speechrate increases, logOdds of schizophrenia decrease.

exp(-0.29826)

# Creating a confusion matrix to estimate performance measures
danish_data$PredictPerc = inv.logit(predict(sr_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 

# We get the following performance numbers:

### Accuracy : 0.57, 0.564
### Sensitivity : 0.427
### Specificity : 0.7
### PPV : 0.564
### NPV : 0.573

rocCurve <- roc(response = danish_data$Diagnosis, predictor = danish_data$PredictPerc)
auc(rocCurve)
ci(rocCurve)
plot(rocCurve, legacy.axes = TRUE)

#Area under the roc curve: 0.586, CI : 0.56 - 0.611



### TESTING OTHER COMBINATIONS OF VARIABLES

## Speech Proportion
prop_pred <- glm(Diagnosis ~ Speech_Prop, family = "binomial", data = danish_data)
summary(prop_pred)


danish_data$PredictPerc = inv.logit(predict(prop_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 
# Insensitive to schizophrenia.



## Coefficient of Variance
CV_pred <- glm(Diagnosis ~ CV, family = "binomial", data = danish_data)
summary(CV_pred)


danish_data$PredictPerc = inv.logit(predict(CV_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 




## Speech Proportion
prop_pred <- glm(Diagnosis ~ Speech_Prop, family = "binomial", data = danish_data)
summary(prop_pred)


danish_data$PredictPerc = inv.logit(predict(prop_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 


## CV * Speechrate
CV_sr_pred <- glm(Diagnosis ~ CV*Speechrate, family = "binomial", data = danish_data)
summary(CV_sr_pred)

danish_data$PredictPerc = inv.logit(predict(CV_sr_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 


## Speech_prop * Speechrate
prop_sr_pred <- glm(Diagnosis ~ Speech_Prop*Speechrate, family = "binomial", data = danish_data)
summary(prop_sr_pred)

danish_data$PredictPerc = inv.logit(predict(prop_sr_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 


## Speech_prop * CV
prop_CV_pred <- glm(Diagnosis ~ Speech_Prop*CV, family = "binomial", data = danish_data)
summary(prop_CV_pred)

danish_data$PredictPerc = inv.logit(predict(prop_CV_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 


## All three

tri_pred <- glm(Diagnosis ~ Speech_Prop*CV*Speechrate, family = "binomial", data = danish_data)
summary(tri_pred)

danish_data$PredictPerc = inv.logit(predict(tri_pred))
danish_data$Predictions[danish_data$PredictPerc>0.5] = "Schizophrenia"
danish_data$Predictions[danish_data$PredictPerc<=0.5] = "Control"
danish_data$Predictions <- danish_data$Predictions %>% as.factor()
confusionMatrix(data = danish_data$Predictions, reference = danish_data$Diagnosis, positive = "Schizophrenia") 

#Basically, only Diagnosis ~ CV offers any real improvement on the initial.

### Cross validating the best models.

# Set seed for reproducibility
set.seed(7)

# Folding the data. "cat_col" specifies a categorical variable that must be balanced in all the folds. "id_col" specifies a variable indicating datapoints belonging to the same ID (thus, they must be in the same fold). This helps us take into account that the experiments is repeated measures (we make up for the fact that we are breaking the asumption of independence).
danish_folds <- fold(danish_data, k = 10, cat_col = "Diagnosis", id_col = "ID") %>% arrange(.folds)

# Glmer cross validation of the Speechrate model
CV1 <- cross_validate(danish_folds, "Diagnosis ~ Speechrate",
                      fold_cols = '.folds',
                      family = 'binomial')
# Show results
summary(CV1)

CV1 %>% select(1:9)

### Balanced Accuracy : 0.562
### Sensitivity : 0.43
### Specificity : 0.695
### PPV : 0.562
### NPV : 0.573
### AUC(ROC) : 0.58 (0.554 - 0.605) 

CV1$ROC[[1]] %>% head()

SensSpec <- CV1$ROC[[1]]

plot((1- SensSpec$Specificities), SensSpec$Sensitivities)
abline(a = 0, b = 1)



CV1$`Confusion Matrix`[[1]]

# A nested tibble with the confusion matrix. The Pos_ columns tells you whether a row is a True
# Positive (TP), True Negative (TN), False Positive (FP), or False Negative (FN), depending on
# which level is the "positive" class. I.e. the level you wish to predict.


## Cross-validating the model using Coefficient of Variance

# Set seed for reproducibility
set.seed(7)

# Folding the data. "cat_col" specifies a categorical variable that must be balanced in all the folds. "id_col" specifies a variable indicating datapoints belonging to the same ID (thus, they must be in the same fold). This helps us take into account that the experiments is repeated measures (we make up for the fact that we are breaking the asumption of independence).
danish_folds <- fold(danish_data, k = 10, cat_col = "Diagnosis", id_col = "ID") %>% arrange(.folds)

## Cross validating the speechrate model
CV1 <- cross_validate(danish_folds, "Diagnosis ~ Speechrate",
                      fold_cols = '.folds',
                      family = 'binomial')
# Show results
summary(CV1)

CV1 %>% select(1:9)

### Balanced Accuracy : 0.562
### Sensitivity : 0.43
### Specificity : 0.695
### PPV : 0.562
### NPV : 0.573
### AUC(ROC) : 0.58 (0.554 - 0.605) 

CV2 %>% select(10:14)

CV2$ROC[[1]] %>% head()

SensSpec <- CV2$ROC[[1]]

plot((1- SensSpec$Specificities), SensSpec$Sensitivities)
abline(a = 0, b = 1)



CV2$`Confusion Matrix`[[1]]

# A nested tibble with the confusion matrix. The Pos_ columns tells you whether a row is a True
# Positive (TP), True Negative (TN), False Positive (FP), or False Negative (FN), depending on
# which level is the "positive" class. I.e. the level you wish to predict.




## Cross validating the CV model
CV2 <- cross_validate(danish_folds, "Diagnosis ~ CV",
                      fold_cols = '.folds',
                      family = 'binomial')
# Show results
summary(CV2)

CV2 %>% select(1:9)

#Balanced Accuracy 0.5883343
#Sensitivity 0.5603544
#Specificity 0.6163142
#Pos Pred Value 0.5704622
#Neg Pred Value 0.6065411
#AUC 0.6170647	
#Lower CI 0.5918323	
#Upper CI 0.6422972


CV2 %>% select(10:14)

CV2$ROC[[1]] %>% head()

SensSpec <- CV2$ROC[[1]]

plot((1- SensSpec$Specificities), SensSpec$Sensitivities)
abline(a = 0, b = 1)



CV2$`Confusion Matrix`[[1]]

# A nested tibble with the confusion matrix. The Pos_ columns tells you whether a row is a True
# Positive (TP), True Negative (TN), False Positive (FP), or False Negative (FN), depending on
# which level is the "positive" class. I.e. the level you wish to predict.


```